Multi-fluids for Representing Sub-filter-scale Convection

### 2020-04-06 submit2/manuscript.tex
Putting figures into a single .ps file per figure

\begin{figure}
\noindent \begin{centering}
\includegraphics[width=1\textwidth]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/resolved/1000/bP}
\par\end{centering}
\noindent \begin{centering}
\includegraphics[width=0.75\textwidth]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/resolved/legends/bP_b}
\par\end{centering}
\caption{The single-fluid, resolved \add[HW]{2D} rising bubble after 1000s. Buoyancy is
coloured and pressure is contoured every $10\text{m}^{2}\text{s}^{-2}$,
negative contours dashed. The $w=0$ contour is dotted.
\label{fig:bubble}}
\end{figure}

@@

\begin{figure}
\noindent %
\begin{tabular}{ccccc}
\begin{turn}{90}
200 Columns
\end{turn} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/resolved/hMean/1000/sigma} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/resolved/hMean/1000/b} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/resolved/hMean/1000/w} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/resolved/hMean/1000/P}\tabularnewline
\begin{turn}{90}
9 Columns
\end{turn} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/nineColumn/hMean/1000/sigma} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/nineColumn/hMean/1000/b} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/nineColumn/hMean/1000/w} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/nineColumn/hMean/1000/P}\tabularnewline
\begin{turn}{90}
5 Columns
\end{turn} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/fiveColumn/hMean/1000/sigma} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/fiveColumn/hMean/1000/b} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/fiveColumn/hMean/1000/w} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/fiveColumn/hMean/1000/P}\tabularnewline
\begin{turn}{90}
3 Columns
\end{turn} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/threeColumn/hMean/1000/sigma} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/threeColumn/hMean/1000/b} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/threeColumn/hMean/1000/w} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/threeColumn/hMean/1000/P}\tabularnewline
\begin{turn}{90}
1 Column
\end{turn} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/singleColumn/hMean/1000/sigma} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/singleColumn/hMean/1000/b} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/singleColumn/hMean/1000/w} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/singleColumn/hMean/1000/P}\tabularnewline
\end{tabular}

\caption{The rising bubble after 1000s simulated with coarse horizontal resolution
and a single-fluid. Horizontal averages are conditioned based on $w$.
\label{fig:bubble_singleUnderRes}}
\end{figure}

@@

\begin{figure}
\setlength{\tabcolsep}{2pt}
\begin{tabular}{cccc}
\multicolumn{4}{c}{\framebox[0.7\linewidth]{\centering
$S_{ij}=0$, \hspace{6pt}
$\gamma=0$, \hspace{6pt}
$C_{D}/r_{c}=0$, \hspace{6pt}
$b_{ij}^{T}=b_{i}$.
}} \tabularnewline 
\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_noTransfer/1000/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_noTransfer/1000/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_noTransfer/1000/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_noTransfer/1000/Pcompare}\tabularnewline
\multicolumn{4}{c}{\framebox[0.7\linewidth]{\centering
$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$, \hspace{6pt}
$\gamma=0$, \hspace{6pt}
$C_{D}/r_{c}=0$, \hspace{6pt}
$b_{ij}^{T}=b_{i}$.
}}\tabularnewline
\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_divTransfer/1000/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_divTransfer/1000/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_divTransfer/1000/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_divTransfer/1000/Pcompare}\tabularnewline
\multicolumn{4}{c}{\framebox[0.7\linewidth]{\centering
$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$, \hspace{6pt}
$\gamma=2.3\!\!\times\!\!10^{4}\text{m}^{2}\text{s}^{-1}$, \hspace{6pt}
$C_{D}/r_{c}=0$, \hspace{6pt}
$b_{ij}^{T}=b_{i}$.
}}\tabularnewline
\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_2p3e4_divTransfer/1000/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_2p3e4_divTransfer/1000/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_2p3e4_divTransfer/1000/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_2p3e4_divTransfer/1000/Pcompare}\tabularnewline
\multicolumn{4}{c}{\framebox[0.7\linewidth]{\centering
$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$, \hspace{6pt}
$\gamma=10^{4}\text{m}^{2}\text{s}^{-1}$, \hspace{6pt}
$C_{D}/r_{c}=0$, \hspace{6pt}
$b_{ij}^{T}=b_{i}$.
}}\tabularnewline
\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer/1000/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer/1000/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer/1000/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer/1000/Pcompare}\tabularnewline
\multicolumn{4}{c}{\framebox[0.7\linewidth]{\centering
$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$, \hspace{6pt}
$\gamma=4\times10^{3}\text{m}^{2}\text{s}^{-1}$, \hspace{6pt}
$C_{D}/r_{c}=0$, \hspace{6pt}
$b_{ij}^{T}=b_{i}$.
}}\tabularnewline
\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e3_divTransfer/1000/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e3_divTransfer/1000/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e3_divTransfer/1000/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e3_divTransfer/1000/Pcompare}\tabularnewline
$\sigma_{1}$ ($\text{m}^3/\text{m}^3$) & $b$ and $b_{i}$ ($\text{m}\text{s}^{-2}$) & $w_{0}$ and $w_{1}$ (m/s) & $P_{0}$ and $P_{1}$ ($\text{m}^2 \text{s}^{-2}$)\tabularnewline
\end{tabular}

\caption{Results of the rising bubble at $t=1000\ \text{s}$. Solid lines are
the multi-fluid, \change[HW]{single}{one} column solutions of the rising bubble. Dashed
lines are the single-fluid, resolved solutions. \label{fig:multiFluidSingleColumn-bad}}
\end{figure}

\begin{figure}
\setlength{\tabcolsep}{2pt}
\begin{tabular}{cccc}
\multicolumn{4}{c}{\framebox[0.8\linewidth]{\centering
$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$, \hspace{6pt}
$\gamma=10^{4}\text{m}^{2}\text{s}^{-1}$, \hspace{6pt}
$C_{D}/r_{c}=1/2000\text{m}^{-1}$, \hspace{6pt}
$b_{ij}^{T}=b_{i}$.
} }\tabularnewline
\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_drag/1000/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_drag/1000/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_drag/1000/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_drag/1000/Pcompare}\tabularnewline
\multicolumn{4}{c}{\framebox[0.7\linewidth]{\centering
$S_{ij}=0$, \hspace{6pt}
$\gamma=10^{4}\text{m}^{2}\text{s}^{-1}$, \hspace{6pt}
$C_{D}/r_{c}=0$, \hspace{6pt}
$b_{ij}^{T}=b_{i}$.
}}\tabularnewline
\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4/1000/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4/1000/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4/1000/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4/1000/Pcompare}\tabularnewline
\multicolumn{4}{c}{\framebox[0.8\linewidth]{\centering
$S_{01}=w_{1}0.2/r_{c}$, \hspace{4pt}
$\gamma=10^{4}\text{m}^{2}\text{s}^{-1}$, \hspace{4pt}
$C_{D}/r_{c}=0/2000\text{m}^{-1}$, \hspace{4pt}
$b_{ij}^{T}=b_{i}$.
}}\tabularnewline
\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_ent/1000/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_ent/1000/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_ent/1000/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_ent/1000/Pcompare}\tabularnewline
\multicolumn{4}{c}{\framebox[0.7\linewidth]{\centering
$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$, \hspace{6pt}
$\gamma=10^{4}\text{m}^{2}\text{s}^{-1}$, \hspace{6pt}
$C_{D}/r_{c}=0$, \hspace{6pt}
$b_{ij}^{T}=0$.
} }\tabularnewline
\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_bT0/1000/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_bT0/1000/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_bT0/1000/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_bT0/1000/Pcompare}\tabularnewline
\multicolumn{4}{c}{\framebox[0.8\linewidth]{\centering
$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$, \hspace{6pt}
$\gamma=10^{4}\text{m}^{2}\text{s}^{-1}$, \hspace{6pt}
$C_{D}/r_{c}=0$, \hspace{6pt}
$b_{ij}^{T}=\frac{1}{2}\left(b_{0}+b_{1}\right)$.
}}\tabularnewline
\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_bT05/1000/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_bT05/1000/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_bT05/1000/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_bT05/1000/Pcompare}\tabularnewline
$\sigma_{1}$ & $b$, $b_{0}$ and $b_{1}$ & $w_{1}$ & $P_{0}$ and $P_{1}$\tabularnewline
\end{tabular}

\caption{\change[HW]{Results of the rising bubble at $t=1000\ \text{s}$. Solid lines are the multi-fluid, single column solutions of the rising bubble. Dashed lines are the single-fluid, resolved solutions.}
{As figure \protect\ref{fig:multiFluidSingleColumn-bad} but different parameterisation options.}
\label{fig:multiFluidSingleColumn}}
\end{figure}

>>>>

\begin{figure}
\noindent \begin{centering}
\includegraphics[width=\textwidth]{figures/bubble.pdf}
\par\end{centering}
\caption{The single-fluid, resolved \add[HW]{2D} rising bubble after \add[HW]{0s, 500s and }1000s. Buoyancy is coloured and pressure is contoured every $10\text{m}^{2}\text{s}^{-2}$,
negative contours dashed. The $w=0$ contour is dotted.
\label{fig:bubble}}
\end{figure}

@@

\begin{figure}
\noindent \begin{centering}
\includegraphics[width=\textwidth]{figures/bubble_singleUnderRes.pdf}
\par\end{centering}
\caption{The rising bubble after 1000s simulated with varying horizontal resolution
and a single-fluid. Horizontal averages are conditioned based on $w$.
\label{fig:bubble_singleUnderRes}}
\end{figure}

@@

\begin{figure}
\noindent
\includegraphics[width=\linewidth]{figures/multiFluidBubble_500_1.pdf}
\caption{Results of the rising bubble at $t=500\ \text{s}$. Solid lines are
the multi-fluid, \change[HW]{single}{one} column solutions of the rising bubble. Dashed
lines are the single-fluid, resolved solutions.
\label{fig:multiFluidBubble_500_1}}
\end{figure}

\begin{figure}
\noindent
\includegraphics[width=\linewidth]{figures/multiFluidBubble_500_2.pdf}
\caption{As figure \ref{fig:multiFluidBubble_500_1} but different parameterisation options.
\label{fig:multiFluidBubble_500_2}}
\end{figure}

\begin{figure}
\noindent
\includegraphics[width=\linewidth]{figures/multiFluidBubble_1000.pdf}
\caption{Results of the rising bubble at $t=1000\ \text{s}$. Solid lines are
the multi-fluid, \change[HW]{single}{one} column solutions of the rising bubble. Dashed
lines are the single-fluid, resolved solutions.
\label{fig:multiFluidBubble_1000}}
\end{figure}
